---
title: "p8105_hw1_sw3455"
author: "Shiying Wu"
date: "2024-09-13"
output: github_document
---
 All the needed package will be download in here.
```{r library, message=FALSE}
library(ggplot2)
library(tidyverse)
```
## Problem 1
  For problem 1, after download `palmerpenguins` package, I read `penguins` data from the package `palmerpenguins`. And then we summary the penguins data in order to collect names and values of these important variables.
```{r summary penguins data problem 0.2}
data("penguins", package = "palmerpenguins")
```
 The penguin data have `r ncol(penguins)` columns which means have `r ncol(penguins)` variables and `r nrow(penguins)` rows means `r nrow(penguins)` observations.The `r ncol(penguins)` variables are `r colnames(penguins)`. 
 
------------------------------------------------------------
*   The `r colnames(penguins)[1]` variable  is contain categorical value of 3 species of penguins, Adelie, Chinstrap, and Gentoo. 

*   The `r colnames(penguins)[2]` variable is also contain categorical value, 3 islan,d that penguins exhibit, including Biscoe, Dream, and Torgersen.

*   The `r colnames(penguins)[3]` variable contain the numerical value of length of penguin length in milliliter in between `r min(pull(penguins, bill_length_mm), na.rm = TRUE)`mm to `r max(pull(penguins, bill_length_mm), na.rm = TRUE)`mm with a mean of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm. 

*   The `r colnames(penguins)[4]` variable contain the numerical value of depth of penguin bill in milliliter in between `r min(pull(penguins, bill_depth_mm),  na.rm = TRUE)`mm to `r max(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm with a mean of `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm. 

*   The `r colnames(penguins)[5]` variable contain the numerical value of length of penguin flipper in milliliter in between `r min(pull(penguins, flipper_length_mm),  na.rm = TRUE)`mm to `r max(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm with a mean of `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. 

*   The `r colnames(penguins)[6]` variable contain the numerical value of weight for penguins in gram in between `r min(pull(penguins, body_mass_g), na.rm = TRUE)`g to `r max(pull(penguins, body_mass_g), na.rm = TRUE)`g with a mean of `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`g. 

*   The `r colnames(penguins)[7]` variable contain categorical value of penguins gender, male and female.

*   The `r colnames(penguins)[8]` variable contain the numerical value of the year for penguins been studies in from `r min(pull(penguins, year), na.rm = TRUE)` to `r max(pull(penguins, year), na.rm = TRUE)`. 

Then I used the ggplot formula to create the plot that `flipper_length_mm` is y and `bill_length_mm` is x with color based on species. The geom_point() is for scatter plot. Due to there are warning based on there are missing value existed in the data, so we used geom_point(na.rm = TRUE) to remove the missing value. 


```{r problem 1 plot, message=FALSE}
ggplot(penguins, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point(na.rm = TRUE)
ggsave("penguins_p1_scatterplot.pdf")
```

## Problem 2
For problem 2, we used the tibble to create data frame that contain four type of variable. And then take mean on each variable to check which type would the mean() works.
```{r problem 2.1}
p2_df = 
  tibble(
    vec_numeric = rnorm(10),
    vec_logic = vec_numeric>0,
    vec_char = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
    vec_factor = factor(c("Apple","Bee","Cat","Apple","Bee","Cat","Apple","Bee","Cat","Apple"))
  )

mean(pull(p2_df, vec_numeric))
mean(pull(p2_df, vec_logic))
mean(pull(p2_df, vec_char))
mean(pull(p2_df, vec_factor))
```
Based on result and warning, we find out that both numeric and logical type could be works by take mean of it, but other two type, character and factor, can not work by take mean of it.

```{r problem 2.2, eval=FALSE}
mean(as.numeric(pull(p2_df, vec_logic)))
mean(as.numeric(pull(p2_df, vec_char)))
mean(as.numeric(pull(p2_df, vec_factor)))
```
The logical type still getting same solution as previous by taking the mean directly. Character type is still not working even after numeric it, all value just transfer into NA. Factor type works on mean() after transfer into numeric value. It transfer into 1,2,and 3, in three factor cases, and then get the mean of it. 